MERF: Morphology-based Entity and Relational Entity Extraction Framework for Arabic \\ ~~ \\ Response to Major Revision

### 2018-04-18 tex/merf/TALMajor/answer/Reviewer1.comments.tex
changes in reviewer comments

\answer{
  We clarified the following notations.... 
  The new notations appear in Section AA in the paper. 
}

@@

\answer{
We modified the description of isA to .... 
}

\itodo{
Add two sentences in the paper to say what isA does. 
}

@@

\answer{
Manual annotators inspected the outcome of the tools and provided 
corrections where tools made mistakes. 
The corrections form the manual gold annotation that we
compared against. 
We indicate that in the Results Section. 
}
\itodo{
  Add teh above to teh results section. 
}

@@

\itodo{
  Ameen will get the size from teh files and provide. 
}

@@

\answer{
A research assistant 6 hours course work and 14 hours 
teaching duties performed the task in two months. 
}
\itodo{
Add this to the results/evaluation
}

>>>>

\answer{
  We clarified the following notations.... 
  The new notations appear in Section AA in the paper. 
}
\itodo{
Pending...
}

@@

\answer{
We modified the description of isA to address this issue. 
Basically, isA is used to detect the `exact match' between a user-chosen value for a morphological feature and the corresponding feature value in a morphological solution of a word.
}

\done{
Add two sentences in the paper to say what isA does.\\ 
Changes are highlighted in red at beginning of Subsection~\ref{subsec:grammar}.
}

@@

\answer{
Manual annotators inspected the outcome of the tools and provided 
corrections where tools made mistakes. 
The corrections form the manual gold annotation that we
compared against. 
We indicate that in the Results Section. 
}
\done{
  Add the above to the results section.\\ 
Done.
}

@@

\itodo{
  Ameen will get the size from the files and provide. 
}

@@

\answer{
A research assistant 6 hours course work and 14 hours 
teaching duties performed the task in two months. 
We clarify this issue in the results Section.
}

\done{
Add this to the results/evaluation.\\
Done
}

### 2018-04-18 tex/merf/TALMajor/answer/Reviewer2.comments.tex
In progress: merging motivation with section 3
changes in reviewer comments

The submitted paper is dealing with an interesting topic 
of knowledge extraction in context of presenting a tool 
for extracting Entities and Relationships from Arabic texts. 
The tool is mainly based on an intensive interactive process, 
where a user has to define tag types, and associates them 
with regular expressions defined over Boolean formulae, 
which are in turn defined over matches of Arabic morphological 
features extended by additional synonyms. 
A major feature of this system is providing the user with a 
user-friendly GUI, however it does not support classification 
tasks.
\answer{
  Thank you for finding our work interesting. 
}

@@

\item \label{Review.2.1} 
The conceptual and implementation aspects of the framework 
were introduced in not clear and differentiated form. 
The authors are advised to separate these issues in formal 
definitions and to present the resulted software tool in 
terms of more clear software techniques.
\answer{
We introduced the following formal definitions...

@@

@@

\item \label{Review.2.3} 
Finally, I believe this framework should be also expressed 
in terms of the complexity and decidability problems, 
particularly when evaluating the required time of different 
development tasks. 
\answer{
  The problem is decidable: RE to FSM. 
  The problem might be not tractable: NDFSM to FSM might 
  be exponential. 
  In practice Table XXX provides runtime results... 
  We modified the paper to include the above. 
}

\item \label{Review.2.4} 
Providing the system with GUI is an advantage, 
However the system requires probably to some extend 
good linguistic and formal languages expertise to optimize 
the benefit of the implements tool.
\answer{
We discuss the target audience of the MERF tool in Section XXX. 
We prepared a set of 45 minutes slides based on the regular
expression chapter in Martin Jurafsky's book to... 
}

>>>>

The submitted paper is dealing with an interesting topic 
of knowledge extraction in context of presenting a tool 
for extracting Entities and Relationships from Arabic texts. 
The tool is mainly based on an intensive interactive process, 
where a user has to define tag types, and associates them 
with regular expressions defined over Boolean formulae, 
which are in turn defined over matches of Arabic morphological 
features extended by additional synonyms. 
A major feature of this system is providing the user with a 
user-friendly GUI, however it does not support classification 
tasks.

\noindent\answer{
  Thank you for finding our work interesting. 
}

@@

\item \label{Review.2.1} 
The conceptual and implementation aspects of the framework 
were introduced in not clear and differentiated form. 
The authors are advised to separate these issues in formal 
definitions and to present the resulted software tool in 
terms of more clear software techniques.

\answer{
We introduced the following formal definitions...

@@

\itodo{
Pending...
}

@@

\item \label{Review.2.3} 
Finally, I believe this framework should be also expressed 
in terms of the complexity and decidability problems, 
particularly when evaluating the required time of different 
development tasks.

\answer{
  The problem is decidable: regular grammar rules to FSM. 
  However, the problem might be not tractable: NDFSM to FSM might 
  be exponential. 
  In practice Table~\ref{tab:results} provides runtime results... 
  We modified the paper to include the above.
}

\done{
Done.
}

\item \label{Review.2.4} 
Providing the system with GUI is an advantage, 
However the system requires probably to some extend 
good linguistic and formal languages expertise to optimize 
the benefit of the implements tool.

\answer{
We discuss the target audience of the MERF tool in Section XXX. 
We prepared a set of 45 minutes slides based on the regular
expression chapter in Martin Jurafsky's book to... 
}

\done{
You note is accurate.
An advantage of the GUI is that it enables a user with mediocre 
linguistic skills to perform information extraction tasks and 
benefit from the framewrok.
}

### 2018-04-18 tex/merf/TALMajor/answer/Reviewer3.comments.tex
changes in reviewer comments

@@

\item \label{Review.3.5}
1-In the introduction, I think you need to omit 
    ``We discuss the importance of the morphological featureotivs supported in 
    MERF terms in Section 3; in brief, morphological preprocessing iskey to 
    Arabic NLP.'' , in page 2 since it will be repeated in page 5.
\answer{
  Done. 
}

@@

@@

\answer{
Up to our knowledge, we introduced the idea. 
We claim that now as a novelty and a contribution in the introduction
and we rephrase the beginning of Section~\ref{sec:synk}. 
}

@@

\answer{
This is a mistake. We corrected that in the paper to 
read as follows... 
}

\itodo{
  Ameen please find where you fixed this and say it here. 
}

@@

\itodo{
  Add that to the Results. 
}

@@

\answer{
  We cleaned the definitions... 
}

\itodo{
  Ameen: highlight the changes and refer to them please. 
}

@@

\itodo{
  Make sure this is moved. 
}

>>>>

\done{
Pending...
}

@@

\item \label{Review.3.5}
1-In the introduction, I think you need to omit 
    ``We discuss the importance of the morphological featureotivs supported in 
    MERF terms in Section 3; in brief, morphological preprocessing iskey to 
    Arabic NLP.'' , in page 2 since it will be repeated in page 5.

@@

\done{
  We combine the Motivation section with \framework section (Now Section~\ref{sec:framework}).
}

@@

\answer{
Up to our knowledge, we introduced the idea. 
We claim that now as a novelty and a contribution in the introduction
and we rephrase the beginning of Section~\ref{subsec:synk}. 
}

@@

\answer{
F is the set of morphological features where each element is in turn a set of the values of that feature.
Hence, A is one such set corresponding to a morphological feature, and CF is a feature value in A.
We clarify this point in Subsection~\ref{subsec:grammar}.
}

\done{
  DONE: Ameen please find where you fixed this and say it here. 
}

@@

\done{
  Add that to the Results.\\
  Added the above explanation in the Results section, needs to be checked.
}

@@

\answer{
  Thank you for pointing it out. We cleaned the definitions.
}

\done{
  highlight the changes and refer to them please.\\
  We use R first to denote the set of user-defined relations.
  Then, we use it to denote the set of MBF tags which is contradicting.
  I got rid of the first case as we don't need it.
}

@@

\done{
  Done: Make sure this is moved. 
}

### 2018-04-18 tex/merf/TALMajor/answer/Reviewer4.comments.tex
changes to answer, colors, and some reviewers addressed
changes in reviewer comments

\item \label{Review.4.1} 
Clarity:   
It is not clear how to associate code actions with 
subexpressions!
\answer{
  We clarify that... 
}

\item \label{Review.4.1} 
Correctness :  
- $Syn^k$ introduces a lot of noise especially if $k$ is large. 
\answer{
  7 is a limit... 
}

\item \label{Review.4.1} 
In the results section, there is no standard evaluation. 
The evaluation is based on comparisons with non-standard 
task-specific tools. 
Also, the reported precision and recall are very sensitive 
to the quality of the annotator!
\answer{
  Same answer to reviewer 3 results... 
}

>>>>

\item \label{Review.4.1} 
Clarity:   
It is not clear how to associate code actions with 
subexpressions!

\answer{
  We elaborate the use of code actions in Subsection~\ref{subsec:numnorm} 
    by introducing Figure~\ref{fig:numnormalgo} and discussing it 
    in the corresponding case study. 
}

\done{
  Discussion of the code actions is pending...
}

\item \label{Review.4.1} 
Correctness :  
- $Syn^k$ introduces a lot of noise especially if $k$ is large.

\answer{
  Your note is accurate, this is why we limit the degree (k) to 7.
  We further elaborate on this by introducing the following in the paper; Subsection~\ref{subsec:grammar}.
  \begin{quote}
  We limit $k$ to a maximum of $7$ since we practically noticed that 
  (1) values above $7$ introduce significant semantic noise and
  (2) the computation is expensive without a bound. 
  \end{quote}
}

\done{
  Done: Use the same answer for Reviewer 3, and say why you used 7. 
}

\item \label{Review.4.1} 
In the results section, there is no standard evaluation. 
The evaluation is based on comparisons with non-standard 
task-specific tools. 
Also, the reported precision and recall are very sensitive 
to the quality of the annotator!

\answer{
  Same answer to reviewer 3 results... 
}

\itodo{
Say something about clarifying the evaluation process. 
}
